---
title: "Lab #0"
author: "Prof Daddysman"
date: "2026-08-26"
format: 
    html:
        embed-resources: true
---

```{r}
#| label: setup
#| purl: false
#| include: false
knitr::opts_chunk$set(
    echo = FALSE, #removes all R code from output
    message = FALSE, #removes all messages
    warning = FALSE #removes all warnings
)
```

```{r}
#| label: metadata
#| purl: true
#----------------------------------------------
# Name: Prof Daddysman
# Date: 2026-08-26
# Purpose: Example qmd for Lab 0 rendering
#----------------------------------------------
```

# Purpose

This document is an example `qmd` (Quarto) file that can be rendered. You will submit this file and the rendered HTML output on Canvas.

# GitHub

My GitHub username is **daddysmanja**.

# Changes

In this document, complete the following:

* In the header information:
    + Change the "author" to your name
    + Update the date if needed
* In the second R code chunk:
    + Change to your name
    + Update the date if needed
* Update your GitHub name in the GitHub section

# Completing the assignment

* Render the file in the console using `quarto::quarto_render("Lab0_Template.qmd")`
* Upload your edited `qmd` file and the `HTML` file created to Canvas
